metric-learn: Metric Learning Algorithms in Python

### 2019-08-07 metric-learn-jmlr.tex

Currently, \texttt{metric-learn} implements 9 popular metric learning algorithms from the literature. Supervised learners include Neighborhood Components Analysis (NCA) (\cite{Goldberger04}), Large Margin Nearest Neighbors (LMNN) (\cite{Weinberger09}), Relative Components Analysis (RCA)\footnote{Strictly speaking, RCA takes as input slightly weaker supervision in the form of \emph{chunklets} (groups of points from the same class).} (\cite{Shental02}), Local Fisher Discriminant Analysis (LFDA) (\cite{Sugiyama07}) and Metric Learning for Kernel Regression (MLKR) (\cite{Weinberger07}). Note that the latter is designed for regression problems and takes as input continuous labels. Pair learners i Mahalanobis Metric for Clustering (MMC) (\cite{Xiang08}), Sparse High-Dimensional Metric Learning (SDML) (\cite{Qi09}), Information Theoretic Metric Learning (ITML) (\cite{Davis07}). For learning on quadruplets: Metric Learning from Relative Comparisons by Minimizing Squared Residual (LSML) (\cite{Liu12}). The details description of these algorithms can be found in the sphinx documentation.

\aurelien{mention flake8 compliance and checks}

>>>>

Currently, \texttt{metric-learn} implements 9 popular metric learning algorithms from the literature. Supervised learners include Neighborhood Components Analysis \citep[NCA,][]{Goldberger04}, Large Margin Nearest Neighbors \citep[LMNN,][]{Weinberger09}, Relative Components Analysis \citep[RCA,][]{Shental02},\footnote{Strictly speaking, RCA takes as input slightly weaker supervision in the form of \emph{chunklets} (groups of points from the same class).} Local Fisher Discriminant Analysis \citep[LFDA,][]{Sugiyama07} and Metric Learning for Kernel Regression \citep[MLKR,][]{Weinberger07}. Note that the latter is designed for regression problems and takes as input continuous labels. Pair learners include Mahalanobis Metric for Clustering (MMC) (\cite{Xing2002a}), Information Theoretic Metric Learning (ITML) (\cite{Davis07}) and Sparse High-Dimensional Metric Learning (SDML) (\cite{Qi09}). Finally, the package implements one quadruplet learner: Metric Learning from Relative Comparisons by Minimizing Squared Residual (LSML) (\cite{Liu12}). Detailed descriptions of these algorithms can be found in the package documentation.
